# Exploratory data analysis

-   Mapping out the underlying structure
-   Identifying the most important variables
-   Univariate visualizations
-   Multivariate visualizations
-   Summary tables

## Visualization

```{r, echo = FALSE, message = FALSE}
library(readxl)
library(readr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(plotly)
```

```{r, echo=FALSE, message = FALSE}
Type_per_year <- read.csv(here::here("Type_per_year.csv"))

Five_common <- Type_per_year %>%
  filter(Type %in% c("Destructions et dégradations volontaires",
                  "Vols sans violence contre des personnes",
                  "Coups et blessures volontaires",
                  "Cambriolages de logement",
                  "Usage de stupéfiants")) 
Five_hist <- Five_common %>%
  group_by(Year, Type) %>%
  summarize(Rate_per_1k = mean(Rate_per_1k, na.rm = TRUE))


```

### Crime

We start by looking at the evolution of the different types of crime by year in France.

```{r, echo=FALSE, message = FALSE}
evol5 <- ggplot(Five_hist) +
  geom_col(aes(x = as.factor(Year), y = Rate_per_1k, fill = Type), position = "dodge") +
  labs(Title= "Evolution of types of crime by year", y = "Rate per thousand", x = "Years")
evol5 <- ggplotly(evol5)
evol5
```

Here we can see that the most common crime in France is deliberate destruction and damage. The effect of the COVID-19 pandemic can also be observed as most crimes have seen an overall drop in 2020. For example, theft without violence saw a sharp drop and it's levels have not gone back to 2019 levels of theft.

```{r, echo=FALSE, message=FALSE}
Plus_minus <- read_csv(here::here("data_end/Crime_to_use.csv"))
view(Plus_minus)

Most <- Plus_minus[-(1)] |> 
  filter(Dep_number %in% c("92","69","13","93","75")) |>
  pivot_longer(as.character(1996:2021), names_to = "Year", values_to = "Tot_crime")


Least <- Plus_minus[-(1)] |> 
  filter(Dep_number %in% c("12","15","50","70","48")) |>
  pivot_longer(as.character(1996:2021), names_to = "Year", values_to = "Tot_crime")


Most_plot <- ggplot(Most, aes(x = as.numeric(Year), y= Tot_crime, color =Dep_number,)) +
  geom_line() +
  labs(Title= "Evolution of crime in the most criminal departments", x= "Year", y= "Total Crime")+
  theme_minimal()

Least_plot <- ggplot(Least, aes(x = as.numeric(Year), y= Tot_crime, color =Dep_number,)) +
  geom_line() +
  labs(Title= "Evolution of crime in the least criminal departments", x= "Year", y= "Total Crime")+
  theme_minimal()

Most_plot <- ggplotly(Most_plot)
Most_plot

Least_plot <- ggplotly(Least_plot)
Least_plot
```



Types of crime comitted also depends on the location. For example we can see in the following two graphs the difference between the Paris departement and the Cher departement. the Cher is a sparsely populated departement.

```{r, echo=FALSE, message=FALSE}
Dep75 <- Five_common %>%
  group_by(Departement, Type, Year) %>%
  summarize(Rate_per_1k= mean(Rate_per_1k, na.rm=TRUE)) %>%
  filter(Departement=="75")

Dep18 <- Five_common %>%
  group_by(Departement, Type, Year) %>%
  summarize(Rate_per_1k= mean(Rate_per_1k, na.rm=TRUE)) %>%
  filter(Departement=="18")

plot75 <-  ggplot(Dep75, aes(x=Year, y=Rate_per_1k, color=Type)) + 
  geom_line() + ggtitle("Types of crime by year in the Paris Region")
plot18 <- ggplot(Dep18, aes(x=Year, y=Rate_per_1k, color=Type)) + 
  geom_line() + ggtitle("Types of crime by year in the Cher departement")

plot75
plot18

```

Here we can see that in Paris, theft without violence is the number one comitted crime. This is surely die to Paris being a big city with many tourists and as such many picpockets. This may not be the case in the Cher region with only 300'000 inhabitants. In the Cher, theft is less prevalent with the biggest Crime Rate being deliberate destruction and damage. Followed by Burglaries.

### Unemployment

Let's now take a look at our first variable: Unemployment. Unemployment in France has evolved through time and has usually been higher than unemployment in Switzerland.

```{r, message=FALSE, echo = FALSE}
Unemployment_T <- read_csv(here::here("Unemployment_T.csv"))

Unemployment_fr <- Unemployment_T[-(1)] |> 
  pivot_longer(-Departement, names_to = "Year", values_to = "Rate") |>
  group_by(Year) |>
  summarize(Rate = mean(Rate)) |>
view(Unemployment_fr)


ggplot(Unemployment_fr, aes(x = Year, y = Rate, group = 1)) + 
  geom_rect(xmin="1990.T3", xmax="1991.T1", ymin=-Inf, ymax = Inf, fill= "gray", alpha = 0.5)+
  geom_text(x="1990.T3", y = 10.2, nudge_x = -0.4, label= "First Gulf War")+
  geom_rect(xmin="2008.T3", xmax="2009.T3", ymin=-Inf, ymax = Inf, fill= "gray", alpha = 0.5)+
  geom_text(x="2007.T3", y = 10.2, label= "2008 crisis")+
  geom_rect(xmin="2020.T1", xmax="2021.T4", ymin=-Inf, ymax = Inf, fill= "gray", alpha = 0.5)+
  geom_text(x="2020.T1", y = 10.1, label= "COVID-19 \n Pandemic")+
  geom_line() +
  labs(title = "Unemployment rate trough the years", y = "Unemployement rate in %") +
  theme(panel.grid = element_blank(), 
        panel.background = element_rect(color = "black", fill = "white")) +
  scale_x_discrete("Years", 
                   breaks = Unemployment_fr$Year[seq(1, nrow(Unemployment_fr), 8)], 
                   labels=seq(1982, 2023, 2))


```
As we can see, Unemployment evolves through the years.


Let's look at the unemployment by Department
```{r, message=FALSE, echo=FALSE}
Unemployment_2022 <- select(Unemployment, Departement, "2022")
colnames(Unemployment_2022) <- c("Departement", "Rate")
Unemp_2022 <- arrange(Unemployment_2022, desc(Rate))

Bars <- ggplot(Unemp_2022, aes(x = reorder(Departement, Rate), y = Rate, fill = Departement)) +
  geom_col() + 
  theme(axis.text.y=element_blank(), legend.position = "none")+
  labs(Title = "Unemployment rate in 2022 by Departement", x = "Rate(%)") +
  theme_minimal() +
  coord_flip()

Bars <- ggplotly(Bars)
Bars
```





